Icicle: fuse your queries

### 2016-04-10 2016fhpc/section/XX-Related.tex
ok

>>>>

Multi-query data analysis\cite{andrade2003efficient} describes a similar problem, where they have multiple queries over the same data that run periodically.
By grouping the multiple queries together, more optimisations can be performed than when treating the queries separately.
This is a lot closer, and performs CSE on expressions like @x = sum(y)@, where @sum@ is a built-in aggregate function.
However, this is only for a small set of built-in aggregates, and does not deal with mutually recursive
